### 2024-04-15 docs/projects/datavis/ggplot/study_session_20240225.qmd
ggplot - rerendered

---
format:
  html: {toc: true, toc-depth: 4, theme: cosmo, output-file: study_session_20240225.html}
code-block-background: true
include-in-header: {text: '<link rel = "icon" href = "data:," />'}

@@

::: {.printedClojure}
```clojure
# A tibble: 234 × 11
   manufacturer model      displ  year   cyl trans drv     cty   hwy fl    class
   &lt;chr&gt;        &lt;chr&gt;      &lt;dbl&gt; &lt;int&gt; &lt;int&gt; &lt;chr&gt; &lt;chr&gt; &lt;int&gt; &lt;int&gt; &lt;chr&gt; &lt;chr&gt;
 1 audi         a4           1.8  1999     4 auto… f        18    29 p     comp…
 2 audi         a4           1.8  1999     4 manu… f        21    29 p     comp…
 3 audi         a4           2    2008     4 manu… f        20    31 p     comp…
 4 audi         a4           2    2008     4 auto… f        21    30 p     comp…
 5 audi         a4           2.8  1999     6 auto… f        16    26 p     comp…
 6 audi         a4           2.8  1999     6 manu… f        18    26 p     comp…
 7 audi         a4           3.1  2008     6 auto… f        18    27 p     comp…
 8 audi         a4 quattro   1.8  1999     4 manu… 4        18    26 p     comp…
 9 audi         a4 quattro   1.8  1999     4 auto… 4        16    25 p     comp…
10 audi         a4 quattro   2    2008     4 manu… 4        20    28 p     comp…
# ℹ 224 more rows

@@

::: {.printedClojure}
```clojure
{:layers
 [{:aes_params [],
   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
   :show.legend [nil],
   :mapping nil,
   :super :ggproto-method,
   :inherit.aes [true],
   :geom_params {:na.rm [false]},
   :geom
   {:non_missing_aes ["size" "shape" "colour"],
    :draw_key :ggproto-method,
    :default_aes
    {:shape [19.0],
     :colour ["black"],
     :size [1.5],
     :fill [nil],
     :alpha [nil],
     :stroke [0.5]},
    :super :ggproto-method,
    :required_aes ["x" "y"],
    :draw_panel :ggproto-method},
   :stat_params {:na.rm [false]},
   :constructor [[$ .MEM xd44ee531f87f4fc5]],
   :position {:compute_layer :ggproto-method, :super :ggproto-method},
   :data []}],
 :scales {:scales [], :super :ggproto-method},
 :mapping {:x [~ cty], :y [~ hwy], :colour [~ year]},
 :theme [],
 :coordinates
 {:expand [true],
  :clip ["on"],
  :limits {:x nil, :y nil},
  :super :ggproto-method,
  :default [true]},
 :facet {:shrink [true], :super :ggproto-method},
 :labels {:x ["cty"], :y ["hwy"], :colour ["year"]}}

@@

<image id="image486" width="1" height="300" xlink:href="data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAAAEAAAEsCAIAAACNMk6CAAAABmJLR0QA/wD/AP+gvaeTAAAAjklEQVQ4jaWTQRKAMAgDd3ik//R1HuOlji3SjNYjhZAEKNt+BCgQIRRIAQRSi2l5hdr79/q1fqBQVw+ErvyipqGH5eh7fNFJi1M+9bC8OT/lrTD9fNYwT/0FpvQzwVju0eObndsd/uUa7qX2NffqNE5w7j7dbCudpXbj2ehX0n3f0ot5pX9/1xkPj79W8p41NH/nSHk1sQAAAABJRU5ErkJggg=="/>

@@

  <use xlink:href="#image486"/>

@@

<g id="surface482">

>>>>

---
format:
  html: {toc: true, toc-depth: 4, theme: cosmo, output-file: study_session_20240225.html}
fontsize: 0.9em
code-block-background: true
include-in-header: {text: '<link rel = "icon" href = "data:," />'}

@@

::: {.printedClojure}
```clojure
# A tibble: 234 × 11
   manufacturer model      displ  year   cyl trans drv     cty   hwy fl    class
   <chr>        <chr>      <dbl> <int> <int> <chr> <chr> <int> <int> <chr> <chr>
 1 audi         a4           1.8  1999     4 auto… f        18    29 p     comp…
 2 audi         a4           1.8  1999     4 manu… f        21    29 p     comp…
 3 audi         a4           2    2008     4 manu… f        20    31 p     comp…
 4 audi         a4           2    2008     4 auto… f        21    30 p     comp…
 5 audi         a4           2.8  1999     6 auto… f        16    26 p     comp…
 6 audi         a4           2.8  1999     6 manu… f        18    26 p     comp…
 7 audi         a4           3.1  2008     6 auto… f        18    27 p     comp…
 8 audi         a4 quattro   1.8  1999     4 manu… 4        18    26 p     comp…
 9 audi         a4 quattro   1.8  1999     4 auto… 4        16    25 p     comp…
10 audi         a4 quattro   2    2008     4 manu… 4        20    28 p     comp…
# ℹ 224 more rows

@@

::: {.printedClojure}
```clojure
{:layers
 [{:aes_params [],
   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
   :show.legend [nil],
   :mapping nil,
   :super :ggproto-method,
   :inherit.aes [true],
   :geom_params {:na.rm [false]},
   :geom
   {:non_missing_aes ["size" "shape" "colour"],
    :draw_key :ggproto-method,
    :default_aes
    {:shape [19.0],
     :colour ["black"],
     :size [1.5],
     :fill [nil],
     :alpha [nil],
     :stroke [0.5]},
    :super :ggproto-method,
    :required_aes ["x" "y"],
    :draw_panel :ggproto-method},
   :stat_params {:na.rm [false]},
   :constructor [[$ .MEM x06c5570df1b44c78]],
   :position {:compute_layer :ggproto-method, :super :ggproto-method},
   :data []}],
 :scales {:scales [], :super :ggproto-method},
 :mapping {:x [~ cty], :y [~ hwy], :colour [~ year]},
 :theme [],
 :coordinates
 {:expand [true],
  :clip ["on"],
  :limits {:x nil, :y nil},
  :super :ggproto-method,
  :default [true]},
 :facet {:shrink [true], :super :ggproto-method},
 :labels {:x ["cty"], :y ["hwy"], :colour ["year"]}}

@@

<image id="image487" width="1" height="300" xlink:href="data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAAAEAAAEsCAIAAACNMk6CAAAABmJLR0QA/wD/AP+gvaeTAAAAjklEQVQ4jaWTQRKAMAgDd3ik//R1HuOlji3SjNYjhZAEKNt+BCgQIRRIAQRSi2l5hdr79/q1fqBQVw+ErvyipqGH5eh7fNFJi1M+9bC8OT/lrTD9fNYwT/0FpvQzwVju0eObndsd/uUa7qX2NffqNE5w7j7dbCudpXbj2ehX0n3f0ot5pX9/1xkPj79W8p41NH/nSHk1sQAAAABJRU5ErkJggg=="/>

@@

  <use xlink:href="#image487"/>

@@

<g id="surface483">
